---
title: "Olympic Predictions for Paris, 2024"
date: 06-07-2024
description: |
  Olympic medal counts: Here's my attempt   
  to predict the gold medal counts based on jet lag
author:
  - name: Dr Steve Jasper
    url: https://jetlagguy.com.au/posts/2024-06-07-paris-olympics
slug: jasper2024parisolympics
creative_commons: CC BY-ND
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Olympic predictions for Paris, 2024

Back in 2021 I published my Tokyo Olympic gold medal predictions (see below), and I think I did fairly well overall. Predicting Olympic gold medals is not an exact
science, and there can be outliers – I can’t predict someone like Steven Bradbury.  However, I have shown that gold medal counts decrease when athletes cross
multiple time zones, and silver medal counts increase (for more information click [here](https://www.frontiersin.org/journals/public-health/articles/10.3389/fpubh.2022.998484/full)). So here are my predictions for the Paris Olympic Games in 2024:

## Biggest winners:

* **France**: expect the home team to do extremely well, in the range of 15 – 20 gold medals
* **Great Britain**: will also do well, no jet lag to deal with. 25 – 30 gold medals.
* **USA**: will do better than Tokyo, 45 – 50 gold medals. Expect even more gold medals at the next Olympics in Los Angeles.

## Biggest losers:

* **Japan**: after hosting, they now have to deal with jet lag. Somewhere from 7-10 gold medals
* **Australia**: jet lag is also an issue for Australia. Again, somewhere from 7-10 gold medals

## Review of previous predictions: Tokyo, 2021

I published my Olympic gold medal predictions before the [Tokyo Olympics in 2021](../2021-07-21-game-of-zones/index.html). Just as now, I went public with my predictions. Here are my predictions, with the actual results:

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Country         | Prediction | Actual | Error |
| :------         | ----------:| ------:| -----:|
| Australia       |     15 ± 2 |     17 |    +2 |
| China           |     40 ± 4 |     38 |    -2 |
| France          |      7 ± 1 |     10 |    +3 |
| Germany         |     14 ± 2 |     10 |    -4 |
| Great Britain   |     18 ± 2 |     22 |    +4 |
| Italy           |      7 ± 1 |     10 |    +3 |
| Japan           |     15 ± 2 |     27 |   +12 |
| Russia (as ROC) |     25 ± 3 |     20 |    -5 |
| South Korea     |     14 ± 2 |      6 |    -8 |
| USA             |     38 ± 4 |     39 |    +1 |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

Mostly pretty good. The only real surprises were just how ***well*** Japan performed as the host nation, and how ***poorly*** South Korea performed. It’s easier to predict for larger nations than smaller ones, and I got the USA within one medal and China within two. I’m giving myself an A- for this assessment.
